---
title: "NLME parameter sampling API"
author: "Venelin Mitov, Daniel Lill, Anne Kümmel, Henning Schmidt"
date: "04.05.2020"
output: 
  slidy_presentation:
    font_adjustment: -1
    footer: Copyright (c) 2020 IntiQuan
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(IQRtools)
library(microbenchmark)

source("../R/14-IQRnlmeParamSampling.R")
source("../R/15-MMVnlmeParamSamplingXLS.R")

set.seed(2)
```

# Introduction

- The sampling of individual parameters has been divided in several functions. 


|Function | Meaning |
|------------------------------|-----------------------------------------------------|
|IQRnlme _readParamXLS|Read NLME model parameter estimates from an excel file|
|IQRnlme _specifyParamSampling|Create an IQRnlmeParamSpec object |
|IQRnlme _sampleParamFromUncertainty| Sample NLME parameters from their uncertainty distribution|
|IQRnlme _sampleRandomEffects|Sample NLME random effects given population parameter values describing the inter-individual variability distribution|
|IQRnlme _sampleIDs|Sample or subset records from a matrix or a data.frame|
|IQRnlme _calcTypicalIndParamValues|Calculate typical individual parameter values by applying covariate formulae to reference population parameter values|
|IQRnlme _calcIndParamValues|Calculate individual parameter values by applying sampled random effects to typical individual parameter values|
|IQRnlme _sampleIndParamValues|Sample individual parameter values, based on a NLME parameter  specification|

---

# Input

Arguments:

- a .xlsx file (`sample_MMVmalariaXLS`) 
  - estimates sheet
  - uncertainty correlation sheet (optional)
- a covariates/regressors data.frame
- Npop
- Nsamples
- FLAG_SAMPLE

---

## Example parameter estimates table {.smaller}
```{r, echo=FALSE, results='asis'}
estimatesTable       <- suppressMessages(suppressWarnings(
  readxl::read_excel(path = "PKparametersNewFormat.xlsx", sheet = "estimates",
                     col_names = TRUE)
))

print(
  xtable::xtable(
    estimatesTable, 
    caption = "Parameter estimates. The same columns are provided as a .csv file or as a sheet 'estimates' in a .xlsx file."), 
  type="html", include.rownames = FALSE)
```

---

## Example uncertainty correlation matrix {.smaller}
```{r, echo=FALSE, results='asis'}
corMatrix       <- suppressMessages(suppressWarnings(
  readxl::read_excel(path = "PKparametersNewFormat.xlsx", sheet = "uncertainty_correlation",
                     col_names = FALSE)
))

print(
  xtable::xtable(
    corMatrix, 
    caption = "Uncertainty distribution correlation matrix on a normal scale. This matrix is provided optionaly as a sheet 'uncertainty_correlation' in the .xlsx file (not available in a .csv file)."),
  type="html", include.rownames = FALSE, include.colnames = FALSE)
```

---

## Example covariates table {.smaller}
```{r, results='asis'}
set.seed(1)
data <- data.frame(
  ID = seq_len(4), 
  WT0 = rlnorm(4, 3, sdlog = 0.2), 
  SEX = sample(c(0, 1), 4, replace = TRUE))
  
print(
  xtable::xtable(
    data, 
    caption = ""), 
  type="html", include.rownames = FALSE)
```
---

# Calling the functions

```{r}
set.seed(1)
fileXLS <- "PKparametersNewFormat.xlsx"

listResultsSampling <- sampleIndParamValues_MMVmalariaXLS(
  fileXLS, 
  Nsamples = 10,
  FLAG_SAMPLE = 1, 
  data = data)
```

---

# Output

An R list with the following members:

|Element | Meaning |
|--------|-----------------------------------------------------|
|`$popParamValues` | a data.frame with a column ID.POP and columns for all [population parameter values](#definitions). For details, see [Step 1](#step-1). |
|`$sampledData` | a data.frame having `Nsample` rows representing sampled records from the patient data. For details, see [Step 2](#step-2). |
| `$typicalIndParamValues` | a data.frame of `Nsample * nrow(popParamValues)` rows, columns `ID.POP` and `ID`, and columns corresponding to the model parameters. The parameter values represent [typical individual parameter values](#definitions) taking into account the corresponding covariate values in `$sampledData`. For details, see [Step 3](#step-3).
| `$randomEffects` | a data.frame of the same dimensionality as `$typicalIndParamValues` containing the [random effects](#definitions) sampled from the IIV distribution (in normal units). For details, see [Step 4](#step-4) |
| `$indParamValues` | a data.frame of the same dimensionality as `$typicalIndParamValues` containing the (final) [individual parameter values](#definitions) in original units. For details, see [Step 5](#step-5) ||
| `$FLAG_SAMPLE` | same as the argument |
| `$Nsamples` | same as the argument |

---

## Example output {.smaller}

```{r, echo=FALSE}
listResultsSampling
```

---

# Speed {.smaller}

## No preprocessing of .xls file {.smaller}
```{r}

microbenchmark(
  
    OldN100 = sample_MMVmalariaXLS(
      filename = fileXLS, 
      Nsamples = 100,
      FLAG_SAMPLE = 1, 
      covariates = data, 
      FLAGid = TRUE),
    NewN100 = IQRnlme_sampleIndParamValues(
      fileXLS, 
      Nsamples = 100,
      FLAG_SAMPLE = 1, 
      data = data),
    
    OldN1000 = sample_MMVmalariaXLS(
      filename = fileXLS, 
      Nsamples = 1000,
      FLAG_SAMPLE = 1, 
      covariates = data, 
      FLAGid = TRUE),
    NewN1000 = IQRnlme_sampleIndParamValues(
      spec = fileXLS, 
      Nsamples = 1000,
      FLAG_SAMPLE = 1, 
      data = data),
    
    times = 5
  
)
```

---

## Preprocessing of .xls file {.smaller}
```{r}
spec <- IQRnlme_specifyParamSampling(fileXLS)

microbenchmark(
  
    OldN100 = sample_MMVmalariaXLS(
      filename = fileXLS, 
      Nsamples = 100,
      FLAG_SAMPLE = 1, 
      covariates = data, 
      FLAGid = TRUE),
    NewN100 = IQRnlme_sampleIndParamValues(
      spec = spec, 
      Nsamples = 100,
      FLAG_SAMPLE = 1, 
      data = data),
    
    OldN1000 = sample_MMVmalariaXLS(
      filename = fileXLS, 
      Nsamples = 1000,
      FLAG_SAMPLE = 1, 
      covariates = data, 
      FLAGid = TRUE),
    NewN1000 = IQRnlme_sampleIndParamValues(
      spec = spec, 
      Nsamples = 1000,
      FLAG_SAMPLE = 1, 
      data = data),
    
    times = 5
  
)
```


# Next steps 

- Testing for IQRtools?
- .Rmd documentation as a chapter in IQRtools book?
- Discuss abstract for M&S Basel?
---

# Known issues

- Sampling from uncertainty of pos.def. matrices.
  
  - Maybe this is a potential point in our presentation.

---

# Thank you!

Questions?
